Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-04 doc/sc2012/legion.tex
spelling
legion
Adding the citation to Keeneland back into the introduction

\item We present results of experiments on three applications:
  fluid-flow on a regular grid, a three-level AMR code solving a
  heat diffusion equation and a circuit simulation.
  We compare each application with best available reference
  versions on three different clusters of multicore processors with
  GPUs, including the Keeneland supercomputer.
%
% FIXME Give the same numbers as in the abstract.
%

@@

\input{circuit}
\input{part_fig}
\input{soop}
\input{mapping}
\input{experiments}
\input{related}
\input{conclusion}

>>>>

\item We present results of experiments on three applications:
  fluid-flow on a regular grid, a three-level AMR code solving a
  heat diffusion equation and a circuit simulation.
  We compare each application with the best reference
  versions on three different clusters of multicore processors with
  GPUs, including the Keeneland supercomputer \cite{Keeneland}.
%
% FIXME Give the same numbers as in the abstract.
%

@@

\input{circuit}
\input{part_fig}
\input{soop}
\input{mapping}
\input{experiments}
\input{related}
%\input{conclusion}
